Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-03-01 sections/methodology.tex
put reference for saturation, and mentioned how we tried to minimize the Hawthorne effect for observation

Each meeting was comprised of two parts: In the first part, we observed them
performing the code review that they had been assigned. To minimize
invasiveness we used only one observer and to encourage the participant to
narrate their work, we asked the participants to think of us as a newcomer to
the team. In this way, most developers thought aloud without need of prompting.
With consent, we recorded the audio, assuring the participants of anonymity.
Since we, as observers, have backgrounds in software development and practices
at Microsoft, we were able to understand most of the work and where and how
information was obtained without inquiry.

@@

Observations also reached a \emph{saturation} point, thus providing insights very similar to the earlier ones. For this, after the first 5-6 observations, we adjusted the meetings to have shorter observations, which we used as a starting point for our meetings and as a ``hook'' to talk about topics in our guideline.

>>>>

Each meeting was comprised of two parts: In the first part, we observed them
performing the code review that they had been assigned. To minimize
invasiveness and the Hawthorne effect, we used only one observer, and to encourage the participant to
narrate their work, we asked the participants to consider him as a newcomer to
the team. In this way, most developers thought aloud without need of prompting.
With consent, we recorded the audio, assuring the participants of anonymity.
Since we, as observers, have backgrounds in software development and practices
at Microsoft, we could understand most of the work and where and how
information was obtained without inquiry.

@@

After the first 5-6 meetings, the observations reached a \emph{saturation} point~\cite{Glas1998a}: They were providing insights very similar to the earlier ones. For this, we adjusted the meetings to have shorter observations, which we used as a starting point for our meetings and as a ``hook'' to talk about topics in our guideline.
